Brain Tumor Detection using Machine Learning Models

### 2021-08-03 backgournd.tex

	Further we propose the use of ML algorithms to overcome the drawbacks of
	traditional classifiers. We investigate and compare the performance of two
	machine learning algorithms namely MLP and Naive Bayes in this work. Since
	these ML algorithms are found to perform well in most of the pattern
	classification tasks. Neural networks are useful as they can learn complex
	mappings between input and output. They are capable of solving much more
	complicated classification tasks. However, when certain rules cannot be
	modeled exactly, the concept of probability is used, which is the basis for
	Naive Bayes classification.

>>>>

	Further we propose the use of ML algorithms to overcome the drawbacks of
	traditional classifiers. We investigate and compare the performance of three
	machine learning models namely CNN, VGG-16 and Resnet-50 in this work. Since
	these ML models are found to perform well in most of the pattern
	classification tasks. Neural networks are useful as they can learn complex
	mappings between input and output. They are capable of solving much more
	complicated classification tasks.

### 2021-08-03 fastai_cnn.tex

\begin{minted}{python}
import numpy as np
import pandas as pd
import torch
import keras
import tensorflow as tf
import os
import gc
import pathlib
from keras.models import Sequential
from keras.layers import Conv2D, MaxPooling2D, Flatten, Dense, Dropout, BatchNormalization
from sklearn.metrics import confusion_matrix
from fastai import *
from fastai.vision.all import *
from fastai.tabular.all import *
from fastai.text.all import *
#from fastai.medical.imaging import *
from fastai.vision.data import ImageDataLoaders
from fastai.vision.models import *
import torchvision.models as models
from fastai.callback.schedule import lr_find
from fastai.callback.schedule import *
from matplotlib import pyplot as plt
from fastai.imports import *
from fastai.torch_core import *
from fastai.learner import *
from sklearn.model_selection import train_test_split
from sklearn.preprocessing import OneHotEncoder

>>>>

\begin{minted}{python}
import numpy as np
import pandas as pd
import torch
import keras
import tensorflow as tf
import os
import gc
import pathlib
from keras.models import Sequential
from keras.layers import Conv2D, MaxPooling2D, Flatten, Dense, Dropout, BatchNormalization
from sklearn.metrics import confusion_matrix
from fastai import *
from fastai.vision.all import *
from fastai.tabular.all import *
from fastai.text.all import *
from fastai.vision.data import ImageDataLoaders
from fastai.vision.models import *
import torchvision.models as models
from fastai.callback.schedule import lr_find
from fastai.callback.schedule import *
from matplotlib import pyplot as plt
from fastai.imports import *
from fastai.torch_core import *
from fastai.learner import *
from sklearn.model_selection import train_test_split
from sklearn.preprocessing import OneHotEncoder
